Untitled

### 2020-07-21 new table formatting.Rmd
simulation design table DONE!
add cover page and insert resized matlab figure in-line.

---
title: "Untitled"
author: "Yuru"
date: "14/07/2020"
output:
  pdf_document: default

editor_options: 
  chunk_output_type: console
---

@@

@@

# insert pdf pictures 
try to insert pdf pictures:

@@

>>>>

---
title: "Untitled"
author: "Yuru"
date: "14/07/2020"
output:
  pdf_document: default
editor_options:
  chunk_output_type: console
---

@@

```{r}
knitr::include_graphics("draft cover page.pdf")
```

\pagebreak

@@

# insert pdf pictures 
try to insert pdf pictures:https://au.mathworks.com/matlabcentral/answers/47357-save-figure-in-a-certain-size

@@

# simulation design table

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|}
\hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^0.5 * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline

\textbf{Assumed Model} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$\\ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
\end{tabular}
\end{table}
